---
params:
  title: DLM Example Presentation
  subtitle: ""
  author: ATLAS Staff
  author_github: https://github.com/jpedroza1228
  author_website: ""
  dlm_website: https://dynamiclearningmaps.org/
  image1_source: https://www.pexels.com/photo/colored-liquids-on-beakers-and-flasks-5427862/
  image2_source: https://unsplash.com/photos/colored-pencil-lined-up-on-top-of-white-surface-l3N9Q27zULw
  image3_source: https://www.pexels.com/photo/person-holding-yellow-and-pink-lego-blocks-298825/
  image4_source: https://www.pexels.com/photo/photo-of-girl-reading-book-3755707/
  image5_source: https://www.pexels.com/photo/brother-and-sister-with-books-on-their-heads-5088188/
title: "`r params$title`"
subtitle: "`r params$subtitle`"
author: "`r params$author`"
date: "`r Sys.Date()`"
format:  
  dlm-quarto-revealjs: default
revealjs-plugins:
    - pointer

---
```{r packages and options}
#| include = FALSE

# library(tidyverse)
# install.packages("")

ggplot2::theme_set(ggplot2::theme_classic())

library(dplyr)
library(tidyr)
library(ggplot2)
library(ratlas)
library(gt)
library(gtExtras)
```

```{r functions}
#| include = FALSE

function(){
  print("Hello world.")
}
```

```{python if using python}
#| include = FALSE

# To use the environment of packages for this quarto document please run
# <conda env create --prefix env -f environment.yml> in your terminal
# conda activate /Users/jonathanpedroza/Documents/r_projects/dlm_template_quarto/env
# conda deactivate

#c onda update -n base -c conda-forge conda
# import numpy as np
# import pandas as pd
# import seaborn as sns

```

```{python python functions}
#| include = FALSE

def function_name():
  print("Hello world.")

```

## Slide 1 - Gonna keep writing things in order to fill the end of the slide

-   Github: [original github template](%60r%20params$github_link%60)

```{r, echo = TRUE, eval = TRUE}
2 + 2
```

::: notes
Speaker notes go here.
:::

## Slide 2

-   put everything that I want to use in the template in the following path

    -   /dlm_template_quarto/dlm_presentation_template_reveal_files/ libs/revealjs/dist/theme/put here

-   more text

::: notes
Speaker notes go here.
:::

## Slide 3

```{r}
#| echo: true
#| eval: false
#| output-location: fragment
#| code-line-numbers: "|1|4"

mtcars |> 
  ggplot(aes(disp, mpg)) +
  geom_point() +
  geom_smooth()
```

```{r}
#| echo: false
#| eval: true

mtcars |> 
  ggplot(aes(disp, mpg)) +
  geom_point() +
  geom_smooth()
```

::: notes
Speaker notes go here.
:::

## Slide 4

::: columns
::: {.column width="40%"}
-   I'm going to keep writing text here until it goes to the second line.

-   Putting a second bullet point to see how well it works with two points per column.
:::

::: {.column width="20%"}
:::

::: {.column width="40%"}
-   This should also go to the second line to see where to put the header here.

-   Putting a second bullet point to see how well it works with two points per column.
:::
:::

::: notes
Speaker notes go here.
:::

## Panel Slides 1

::: panel-tabset
## Output

```{r}
#| eval: true
#| echo: false

ggplot(mtcars,
  aes(cyl, wt)) +
  geom_point(color = "dodgerblue",
    position = position_jitter(width = .3)) +
  theme_minimal()
```

## Code

```{r}
#| eval: false
#| echo: true

ggplot(mtcars,
  aes(cyl, wt)) +
  geom_point(color = "dodgerblue",
    position = position_jitter(width = .3)) +
  theme_minimal()
```
:::

::: notes
Speaker notes go here.
:::

## Panel Slides 2

::: panel-tabset
## Output

```{r}
#| eval: true
#| echo: false

ggplot(mtcars,
  aes(cyl)) +
  geom_bar(fill = "dodgerblue") +
  theme_minimal()
```

## Code

```{r}
#| eval: false
#| echo: true

ggplot(mtcars,
  aes(cyl)) +
  geom_bar(fill = "dodgerblue") +
  theme_minimal()
```
:::

::: notes
Speaker notes go here.
:::

## Incremental Slides

::: incremental
-   First item
-   Second item
:::

::: notes
Speaker notes go here.
:::

## Table Slide {.table-background}

```{r}
mtcars |> 
  group_by(as.factor(cyl)) |>
  summarize(
    avg_mpg = mean(mpg, na.rm = TRUE),
    avg_hp = mean(hp, na.rm = TRUE),
    across(
      matches("avg"),
      ~round(.x)
    )
  ) |>
  gt(
    id = "table"
  ) |>
 tab_options(table.width = pct(100)) |>
 opt_interactive(
   use_pagination = TRUE,
   use_search = TRUE,
   use_resizers = TRUE,
   use_highlight = TRUE,
   use_compact_mode = TRUE, 
   use_text_wrapping = TRUE,
   use_page_size_select = TRUE
 )
```

::: notes
Speaker notes go here.
:::

## Image Slide

![](%60r%20params$image1%60)

## Contact Information

-   `r params$author`

    -   GitHub: [GitHub link](%60r%20params$github_link%60)
    -   Website: [DLM Site](%60r%20params$dlm_website%60)

-   Image Sources:

    -   [image1_source](%60r%20params$image1_source%60)

::: notes
Speaker notes go here.
:::